\bf Forecast reconciliation: A geometric view with new insights on bias correction

### 2019-09-05 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Updated appendices

Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{S}\bm{G}\bm{S}=\bm{S}$ or alternatively that $\bm{G}\bm{S}=\bm{I}$. Both of these conditions are equivalent to assuming that $\bm{S}\bm{G}$ is a projection matrix (see Section~\ref{app:projection-proof} in the Appendix for a proof). However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{G}\bm{S}=\bm{I}$. This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner. However, equipped with a geometric understanding of the problem, we would advise against this approach. The constraint $\bm{G}\bm{S}=\bm{I}$ is not just about bias. Dropping the constraint compromises all of the attractive properties of projections. It also opens the door to reconciliation methods that change already coherent base forecasts, which suggests an increase in the variability of the forecasts. This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance.

@@

We consider ``overnight trips'' across Australia as a measure of domestic tourism flows. The data are provided by the National Visitor Survey and are collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more. We disaggregate tourism flows into 7 states, 27 zones and 75 regions forming a natural geographical hierarchy that is of interest to tourism operators and policy makers amongst others. Hence, there are $110$ series across the hierarchy with $75$ bottom-level series. More information about the series and the geographical hierarchy is presented in Table~\ref{table:A1} in the Appendix. The data span the period January 1998 to December 2017, which gives a total of $240$ observations per series.

@@

\clearpage

@@

To establish the first statement let $\bm{s}_j$ be the $j^{th}$ column of $\bm{S}$. Since by definition, $\bm{s}_j$ lies in $\mathfrak{s}$, it must hold that $\bm{S}\bm{G}\bm{s}_j=\bm{s}_j$. Stacking these vectors horizontally
\begin{align*}
\bm{S}\bm{G}\bm{S}
  & = \begin{pmatrix}
        \bm{S}\bm{G}\bm{s}_1, & \bm{S}\bm{G}\bm{s}_2, & \cdots & \bm{S}\bm{G}\bm{s}_m
      \end{pmatrix} \\
  & = \begin{pmatrix}
        \bm{s}_1, & \bm{s}_2, & \cdots & \bm{s}_m
      \end{pmatrix}\\
  & = \bm{S}.
\end{align*}

To establish the converse it suffices to postmultiply the condition $\bm{S}\bm{G}\bm{S}=\bm{S}$ by $\bm{G}$. This yields $\bm{S}\bm{G}\bm{S}\bm{G}=\bm{S}\bm{G}$ which in turn implies idempotence since $(\bm{S}\bm{G})^2=\bm{S}\bm{G}$.

>>>>

Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{S}\bm{G}\bm{S}=\bm{S}$ or alternatively that $\bm{G}\bm{S}=\bm{I}$. Both of these conditions are equivalent to assuming that $\bm{S}\bm{G}$ is a projection matrix (see Section~\ref{app:projection-proof} in Appendix A for a proof). However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{G}\bm{S}=\bm{I}$. This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner. However, equipped with a geometric understanding of the problem, we would advise against this approach. The constraint $\bm{G}\bm{S}=\bm{I}$ is not just about bias. Dropping the constraint compromises all of the attractive properties of projections. It also opens the door to reconciliation methods that change already coherent base forecasts, which suggests an increase in the variability of the forecasts. This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance.

@@

We consider ``overnight trips'' across Australia as a measure of domestic tourism flows. The data are provided by the National Visitor Survey and are collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more. We disaggregate tourism flows into 7 states, 27 zones and 75 regions forming a natural geographical hierarchy that is of interest to tourism operators and policy makers amongst others. Hence, there are $110$ series across the hierarchy with $75$ bottom-level series. More information about the series and the geographical hierarchy is presented in Table~\ref{table:A1} in Appendix B\@. The data span the period January 1998 to December 2017, which gives a total of $240$ observations per series.

@@

\clearpage
\appendix

@@

To establish the first statement, let $\bm{s}_j$ be the $j$th column of $\bm{S}$. Since by definition, $\bm{s}_j$ lies in $\mathfrak{s}$, it must hold that $\bm{S}\bm{G}\bm{s}_j=\bm{s}_j$. Stacking these vectors horizontally
\begin{align*}
\bm{S}\bm{G}\bm{S}
  & = \begin{pmatrix}
        \bm{S}\bm{G}\bm{s}_1, & \bm{S}\bm{G}\bm{s}_2, & \cdots & \bm{S}\bm{G}\bm{s}_m
      \end{pmatrix} \\
  & = \begin{pmatrix}
        \bm{s}_1, & \bm{s}_2, & \cdots & \bm{s}_m
      \end{pmatrix}\\
  & = \bm{S}.
\end{align*}

To establish the converse it suffices to postmultiply the condition $\bm{S}\bm{G}\bm{S}=\bm{S}$ by $\bm{G}$. This yields $\bm{S}\bm{G}\bm{S}\bm{G}=\bm{S}\bm{G}$, which in turn implies idempotence since $(\bm{S}\bm{G})^2=\bm{S}\bm{G}$.
